Automated Synthesis of State-Space Digital Systems

### 2016-12-21 cav2017/cav2017.tex
review introduction

Linear Time Invariant Control systems represent a sizeable portion of
modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
environmental control, navigation and
robotics~\cite{astrom1997computer,Franklin15}.

Correct and sound control is non-trivial, however. The problem is
exacerbated by artefacts specific to digital control, such as the
effects of finite-precision arithmetic, time discretization, and
quantization noise introduced by A/D and D/A conversion.  Thus, the
programming is a key barrier to broad adoption of digital control, and
requires considerable expertise.

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability, working typically on continuous domains
\cite{sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.  Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis\cite{cimatti2013parameter}.

In this paper, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant alongside the discrete domain of the controller and the
hybrid elements that communicate them.

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS) which makes use 
of Counter-Example Guided Abstraction Refinement (CEGAR)
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

>>>>

Linear Time Invariant (LTI) control systems represent a sizeable portion of
modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
environmental control, navigation, and 
robotics~\cite{astrom1997computer,Franklin15}.
Correct and sound control system verification is a challenging task. 
In particular, the verification problem is exacerbated by artifacts specific 
to digital control, such as the effects of finite-precision arithmetic, 
time discretization, and quantization noise, which are typically introduced 
by Analog-to-Digital (A/D) and Digital-to-Analog (D/A) conversion.  
Thus, the programming is a key barrier to broad adoption of digital control, 
and requires considerable expertise.

Whilst there is a vast literature in validation of control systems,
the subject of control synthesis has been somewhat restricted in the
properties it explores.  Traditionally, this focuses mainly on the
subject of stability, working typically on continuous domains
\cite{sadabadi2016static}, or using switched
models~\cite{DBLP:conf/emsoft/RavanbakhshS16}.  Reachability tools are
also used when discretizing the state-space for both verification and
parametric synthesis~\cite{cimatti2013parameter}.
In this paper, however, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant, alongside the discrete domain of the controller and the
hybrid elements that communicate them.

To this end, we formalise the notion of solution generalisation for
Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
of Counter-Example Guided Abstraction Refinement (CEGAR),
%on simplified abstractions of the system
in order to achieve scalability.
This strategy enables the inductive generalisation engine inside CEGIS
to look for candidate solutions in a reduced solution space.  %% The
%% latter case is a well know technique for abstract interpretation that
%% allows simplification of the procedures over a sound abstraction of
%% the verification model.

\textcolor{red}{Cristina: Can you please further expand the introduction
by adding more details about our synthesis approach to control systems?}
